A Minimal Demo of \texttt{glyphmaps}

### 2012-06-04 paper/paper.Rnw
editing paper
paper changes

\texttt{ply$\_$aes} doesn't actually create embedded plots, but is closely related to the glyphing process. By default, \texttt{ggplot2} does not calculate statistics in a groupwise manner. However, such calculations can be useful in certain situations. For example, \texttt{ply$\_$aes} is built into \texttt{glyph} and \texttt{grid} by default; embedded plots quickly become boring when aesthetics do not vary from subplot to subplot. Groupwise aesthetics can be interesting in other situations as well. For example, Figure~\ref{fig:groupwise2} demonstrates how groupwise aesthetics can be used to avoid overplotting.
<<groupwise2, fig.width = 4, fig.height = 3, out.width = 0.49\textwidth, cache = TRUE, tidy = FALSE, fig.caption = '\texttt{ply$\_$aes} provides another way to deal with overplotting.'>>=
## overplotted
ggplot() + geom_point(aes(x = temperature, y = ozone, color = lat), data = nasa)  
# using ply_aes to plot just summaries
ggplot() + ply_aes(geom_point(aes(x = mean(temperature), y = mean(ozone), 
  color = lat[1]), data = nasa), c("lat", "long"))
@

@@

## facetted plot
system.time(print(ggplot(nasa) + glyph(geom_point(aes(x = surftemp, 
  y = temperature), size = 1/2) + facet_grid(long~lat))))
@

>>>>

\texttt{ply$\_$aes} doesn't actually create embedded plots, but is closely related to the glyphing process. By default, \texttt{ggplot2} does not calculate statistics in a groupwise manner. However, such calculations can be useful in certain situations. For example, \texttt{ply$\_$aes} is built into \texttt{glyph} and \texttt{grid} by default; embedded plots quickly become boring when aesthetics do not vary from subplot to subplot. Groupwise aesthetics can be interesting in other situations as well. For example, Figure~\ref{fig:groupwise2} demonstrates how groupwise aesthetics can be used to avoid overplotting.
<<groupwise2, fig.width = 4, fig.height = 3, out.width = 0.49\textwidth, cache = TRUE, tidy = FALSE, fig.caption = '\texttt{ply$\_$aes} provides another way to deal with overplotting.'>>=
## overplotted
ggplot() + geom_point(aes(x = temperature, y = ozone, color = lat), data = nasa, size = 1/2)  
# using ply_aes to plot just summaries
ggplot() + ply_aes(geom_point(aes(x = mean(temperature), y = mean(ozone), 
  color = lat[1]), data = nasa, size = 1/2), c("lat", "long"))
@

@@

## facetted plot
system.time(print(ggplot(nasa) + geom_point(aes(x = surftemp, 
  y = temperature), size = 1/2) + facet_grid(long~lat))))
@
